An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2023-06-19 poly-embed-journal/poly-embed-journal.tex
tweaks, pass

\documentclass[twoside,11pt]{article}
\usepackage[natbib]{jmlr2e}
\PassOptionsToPackage{numbers, compress, sort}{natbib}
\usepackage[margin=1.1in]{geometry}

@@

\newcommand{\regret}[3]{R_{#1}(#2,#3)}

@@

\jmlrheading{1}{2022}{1-55}{7/22}{7/22}{finocchiaro22a}{Jessie Finocchiaro, Rafael M. Frongillo, and Bo Waggoner}

@@

%\title{An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates}
%\author{%
% Jessie Finocchiaro \\
% \texttt{jefi8453@colorado.edu}\\
% University of Colorado Boulder
% \and
% Rafael Frongillo\\
% \texttt{raf@colorado.edu}\\
%  University of Colorado Boulder
% \and
% Bo Waggoner\\
% \texttt{bwag@colorado.edu}\\
%  University of Colorado Boulder
%}
%%\date{%                          % nice hack
%%  % \vspace*{-5pt}
%%  University of Colorado Boulder
%%  \\[15pt]
%%  \today
%%}
\begin{document}
\title{An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates}
\author{\name Jessie Finocchiaro \email jefi8453@colorado.edu \\
	\addr Department of Computer Science\\
	University of Colorado Boulder\\
	Boulder, CO, USA
	\AND
	\name Rafael M. Frongillo \email raf@colorado.edu \\
	\addr Department of Computer Science\\
	University of Colorado Boulder\\
	Boulder, CO, USA
	\AND
	\name Bo Waggoner \email bwag@colorado.edu \\
	\addr Department of Computer Science\\
	University of Colorado Boulder\\
	Boulder, CO, USA
}

@@

\subsection{Surrogate regret bounds}\label{subsec:regret-bounds}
Recall that the approach of surrogate risk minimization is to learn a hypothesis $h$ that minimizes expected surrogate loss, then output hypothesis $\psi \circ h$, which hopefully minimizes expected target loss.
We would like surrogates where a bound on surrogate loss of $h$ immediately implies a bound on target loss of $\psi \circ h$.
One can formalize this problem in terms of \emph{regret}, as follows.
Fix a data distribution $\D$.
The \emph{surrogate regret} $R_L$ of $h$ and the \emph{target regret} $R_{\ell}$ of the implied hypothesis $\psi \circ h$, are given by
\begin{align*}
  R_L(h;\D) &= \E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} \E_{(X,Y)\sim\D} L(h'(X))_Y~,
  \\
  R_\ell(\psi\circ h;\D) &= \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{g':\X\to\R} \E_{(X,Y)\sim\D} \ell(g'(X))_Y~,
\end{align*}
% $R_L(h;\D) = \E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} \E_{(X,Y)\sim\D} L(h'(X))_Y$,
where the infimum is taken over all measurable functions.
The infimum represents the risk of the Bayes optimal hypothesis, so regret can be viewed as \emph{excess risk} under the assumption that the learner's hypothesis class contains the Bayes optimal.
%(One may equivalently assume the Bayes optimal hypothesis is in the function class.)
% Given $h$, the \emph{target regret} of the implied hypothesis $\psi \circ h$ is $R_\ell(\psi\circ h;\D) = \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} \E_{(X,Y)\sim\D} \ell(h'(X))_Y$.

Consistency (Definition~\ref{def:consistency}) means that if the surrogate regret of $h$ converges to zero, then the target regret of $\psi \circ h$ does as well; in other words, $R_L(h;\D) \to 0$ implies $R_{\ell}(\psi \circ h;\D) \to 0$.
Consistency is therefore a minimal requirement; in general, we are also interested in the \emph{rate} at which the target regret diminishes, as a function of the number of data points $m$.
A \emph{regret transfer bound}, also called a \emph{surrogate regret bound}, gives a guarantee on the relationship between the rates of convergence of $R_L$ and $R_{\ell}$.
For example, a surrogate with a fast rate of convegence $R_L \to 0$ as $m \to \infty$ is not very useful if we nevertheless have a slow rate $R_{\ell} \to 0$.

We show that, for any polyhedral surrogate, the transfer is linear: if surrogate regret diminishes at a rate of $O(f(m))$, then the target rate is also $O(f(m))$.
In particular, fast convergence in surrogate regret implies fast convergence in target regret.
\begin{theorem}
  \label{thm:linear-regret-bound}
  Let $(L,\psi)$ be consistent for a discrete loss $\ell$, and $L$ polyhedral.
  Then there exists $c > 0$ such that, for all hypotheses $h$ and data distributions $\D$, we have $R_{\ell}(\psi \circ h;\D) \leq c \cdot R_L(h;\D)$.
\end{theorem}
In the proof (\S~\ref{app:regret-bounds}), we further show that the constant $c$ can be decomposed in terms of three constants, which depend on $L$, $\psi$, and $\ell$, respectively.
Specifically, we may write $c = C_\ell H_L / \epsilon_\psi$, where $H_L$ is the Hoffman constant for $L$, $\epsilon_\psi$ the separation of $\psi$, and $C_\ell$ the maximum loss gap of $\ell$.
This expression gives the intuition that larger link separation is generally better for performance.
In some cases, this bound can be tightened, as we discuss in \S~\ref{sec:regret-tighter-bounds}.
See \citet{frongillo2021surrogate} for a quadratic lower bound on the rate transfer for sufficiently non-polyhedral surrogates.

@@

Throughout we will work with the two \emph{regret} functions:
the \emph{surrogate regret} $R_L(u,p) = \inprod{p}{L(u)} - \risk{L}(p)$, and similarly the \emph{target regret} $R_{\ell}(r,p) = \inprod{p}{\ell(r)} - \risk{\ell}(p)$.
We will use these functions again when we prove surrogate regret bounds (\S~\ref{app:regret-bounds}).
% In fact, the results in this section can be extended to surrogate regret bounds; see \citet{frongillo2021surrogate}.

@@

\begin{lemma}\label{lem:hoffman-polyhedral}
  Let $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral loss with $\Gamma = \prop{L}$.
  Then for any fixed $p$, there exists some smallest constant $H_{L,p} \geq 0$ such that $d_{\infty}(u,\Gamma(p)) \leq H_{L,p} R_L(u,p)$ for all $u \in \reals^d$.
\end{lemma}
\begin{proof}
  Since $L$ is polyhedral, there exist $a_1,\ldots,a_m \in \reals^d$ and $c\in\reals^m$ such that we may write $\inprod{p}{L(u)} = \max_{1\leq j\leq m} a_j \cdot u + c_j$.
  Let $A \in \reals^{m\times d}$ be the matrix with rows $a_j$, and let $b = \risk{L}(p)\ones - c$, where $\ones\in\reals^m$ is the all-ones vector.
  Then we have
  \begin{align*}
    S(A,b)
    &:= \{u\in\reals^d \mid A u \leq b\}
    \\
    &= \{u\in\reals^d \mid A u + c \leq \risk{L}(p)\ones\}
    \\
    &= \{u\in\reals^d \mid \forall i\, (A u + c)_i \leq \risk{L}(p)\}
    \\
    &= \{u\in\reals^d \mid \max_i \;(A u + c)_i \leq \risk{L}(p)\}
    \\
    &= \{u\in\reals^d \mid \inprod{p}{L(u)} \leq \risk{L}(p)\}
    \\
    & = \Gamma(p)~.
  \end{align*}
  Similarly, we have $\max_i\; (A u - b)_i = \inprod{p}{L(u)} - \risk{L}(p) = \regret{L}{u}{p} \geq 0$.
  Thus,
  \begin{align*}
    \|(Au - b)_+\|_\infty
    &= \max_i\; ((Au - b)_+)_i
    \\
    &= \max((Au - b)_1,\ldots,(Au - b)_m, 0)
    \\
    &= \max(\max_i\; (Au - b)_i, \, 0)
    \\
    &= \max_i\; (Au - b)_i
    % \\
    % &= \inprod{p}{L(u)} - \risk{L}(p)
    \\
    &= \regret{L}{u}{p}~.
  \end{align*}
  Now applying Theorem~\ref{thm:hoffman}, we have
  \begin{align*}
    d_\infty(u,\Gamma(p))
    &=    d_\infty(u,S(A,b))
    \\
    &\leq H(A) \|(Au-b)_+\|_\infty
    \\
    &= H(A) \regret{L}{u}{p}~.
  \end{align*}
\end{proof}

Given discrete loss $\ell: \R \to \reals_+^{\Y}$, define the constant $C_{\ell} = \max_{r,r' \in \R, y \in \Y} \ell(r)_y - \ell(r')_y$.
We are now ready to prove Theorem \ref{thm:calibrated-separated}.
\calibratedseparated*
\begin{proof}
  Let $\gamma=\prop{\ell}$ and $\Gamma=\prop{L}$.
  From Lemma~\ref{lem:calibrated-eps-sep}, calibration implies $\epsilon$-separation.
  For the converse, suppose $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$.
  Fix $p\in\simplex$.
  To show calibration, it suffices to find a positive lower bound for $R_L(u,p)$ that holds for all $u\in\reals^d$ with $\psi(u) \notin \gamma(p)$.

  Applying the definition of $\epsilon$-separated and Lemma~\ref{lem:hoffman-polyhedral}, $\psi(u) \notin \gamma(p)$ implies
  \begin{align*}
    \epsilon &\leq    d_{\infty}(u,\Gamma(p)) \leq H_{L,p} R_L(u,p) \implies 1 \leq \frac{H_{L,p}}{\epsilon} R_L(u,p)~.
  \end{align*}
  Let $C_{\ell} = \max_{r,p} R_{\ell}(r,p)$.
  Then $R_{\ell}(\psi(u),p) \leq C_{\ell} \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p)$.

  If $H_{L,p} = 0$, then for all $u\in\reals^d$ we have $R_\ell(\psi(u),p) = 0$, so calibration for this $p$ is trivial.
  \btw{In fact, we must also have $\Gamma(p) = \reals^d$ by Lemma~\ref{lem:hoffman-polyhedral}, since every $u\in\reals^d$ would have $d_\infty(u,\Gamma(p)) = 0$ and $\Gamma(p)$ is closed.}
  Similarly, if $C_\ell = 0$, then $R_\ell(r,p) = 0$ for all $r\in\R$, so again $R_\ell(\psi(u),p) = 0$ for all $u\in\reals^d$.

  Now assume $C_\ell > 0$ and $H_{L,p} > 0$.
  Let $C'_{\ell,p} \doteq \min_{r \notin \gamma(p)} R_\ell(r,p) > 0$.
  (As we assume $C_\ell > 0$, we must have $\gamma(p) \neq \R$, so the minimum is attained.)
  Then for all $u$ such that $\psi(u) \notin \gamma(p)$, we have $R_\ell(\psi(u),p) \geq C'_{\ell,p}$.
  Rearranging, we have
  \[ \psi(u) \notin \gamma(p) \implies R_L(u,p) \geq \frac{C'_{\ell,p} \epsilon}{C_\ell H_{L,p}} > 0~.\]
  Thus, $\inf_{u : \psi(u) \notin \gamma(p)} \inprod{L(u)}{p} > \risk{L}(p)$.
  Since the above holds for all $p\in\simplex$, $\psi$ is calibrated.
\end{proof}

@@

\subsection{Proof of Theorem~\ref{thm:linear-regret-bound}}
% The following is a direct result of Jensen's inequality, using the fact that $R_L(h;\D) = \E_X R_L(h(X),p_X)$ where $p_X$ is the conditional distribution on $Y$ given $X$.
% \begin{observation} \label{obs:transfer}
%   If $(L,\psi)$ guarantee a conditional regret transfer of $\zeta$ for $\ell$, and $\zeta$ is concave, then $(L,\psi)$ guarantee a regret transfer of $\zeta$ for $\ell$.
% \end{observation}

\begin{lemma}\label{lem:linear-on-levelset}
  Suppose $(L,\psi)$ indirectly elicits $\ell$ and let $\Gamma = \prop{L}$.
  Then for any fixed $u,u^* \in \reals^d$ and $r \in \R$, the functions $R_L(u,\cdot)$ and $R_{\ell}(r,\cdot)$ are linear in their second arguments on $\Gamma_{u^*}$.
\end{lemma}
\begin{proof}
  Let $u^* \in \reals^d$ and $p \in \Gamma_{u^*}$.
  By definition, for all $p \in \Gamma_{u^*}$, $\risk{L}(p) = \inprod{p}{L(u^*)}$.
  So for fixed $u$,
    \[ R_L(u,p) = \inprod{p}{L(u)} - \inprod{p}{L(u^*)} = \inprod{p}{L(u) - L(u^*)} , \]
  a linear function of $p$ on $\Gamma_{u^*}$.
  Next, by the definition of indirect elicitation, there exists $r^*$ such that $\Gamma_{u^*} \subseteq \gamma_{r^*}$.
  By the same argument, for fixed $r$, $R_{\ell}(r,p) = \inprod{p}{\ell(r) - \ell(r^*)}$, a linear function of $p$ on $\gamma_{r^*}$ and thus on $\Gamma_{u^*}$.
\end{proof}

@@

\begin{lemma}\label{lem:separated-constant-p}
  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
  If $(L,\psi)$ indirectly elicit $\ell$ and $\psi$ is $\epsilon$-separated, then for all $u$ and $p$,
    \[ R_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p) . \]
\end{lemma}
\begin{proof}
  If $\psi(u) \in \gamma(p)$, then $R_{\ell}(u,p) = 0$ and we are done.
  Otherwise, applying the definition of $\epsilon$-separated and Lemma~\ref{lem:hoffman-polyhedral},
  \begin{align*}
    \epsilon &<    d_{\infty}(u,\Gamma(p))  \\
             &\leq H_{L,p} R_L(u,p) .
  \end{align*}
  So $R_{\ell}(\psi(u),p) \leq C_{\ell} \leq \frac{C_{\ell} H_{L,p}}{\epsilon} R_L(u,p)$.
\end{proof}

We can now restate and prove Theorem~\ref{thm:linear-regret-bound}.
\begin{theorem}[Theorem~\ref{thm:linear-regret-bound}]
  Let $\ell: \R \to \reals_+^{\Y}$ be discrete, $L: \reals^d \to \reals_+^{\Y}$ polyhedral, and $\psi: \reals^d \to \R$.
  If $(L,\psi)$ are consistent for $\ell$, then there exists constants $\epsilon_\psi, H_L > 0$ such that
    \[ (\forall h,\D) \quad R_{\ell}(\psi \circ h ; \D) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} R_L(h ; \D) ~. \]
\end{theorem}
\begin{proof}
  Let $\Gamma = \prop{L}$.
  From Lemma~\ref{lem:X}, there is a finite set $U \subset \reals^d$ of predictions such that (a) for each $u \in U$, the level set $\Gamma_u$ is a polytope (see e.g.\ Lemma~\ref{lem:level-set-is-projected-face}), and (b) $\cup_{u \in U} \Gamma_u = \simplex$.
  For each $u\in U$ let $\mathcal{Q}_u \subset \simplex$ be the finite set of vertices of the polytope $\Gamma_u$, and define the finite set $\mathcal{Q} = \cup_{u \in U} \mathcal{Q}_u$.
  Let $H_L := \max_{q\in\mathcal{Q}} H_{L,q}$.

>>>>

\documentclass[twoside,11pt]{article}
\usepackage[natbib,preprint]{jmlr2e-hack} %% FIX BEFORE SUBMITTING
\PassOptionsToPackage{numbers, compress, sort}{natbib}
\usepackage[margin=1.1in]{geometry}

@@

\newcommand{\Reg}{\mathrm{Reg}}
\newcommand{\regret}[3]{\Reg_{#1}(#2,#3)}

@@

% \jmlrheading{2023}{accepted with minor revisions}{1-56}{7/22}{?/23}{finocchiaro22a}{Jessie Finocchiaro, Rafael Frongillo, and Bo Waggoner}
\jmlrheading{1}{2023}{1-55}{7/22}{7/22}{finocchiaro22a}{Jessie Finocchiaro, Rafael M. Frongillo, and Bo Waggoner}

@@

%\title{An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates}
%\author{%
% Jessie Finocchiaro \\
% \texttt{jefi8453@colorado.edu}\\
% University of Colorado Boulder
% \and
% Rafael Frongillo\\
% \texttt{raf@colorado.edu}\\
%  University of Colorado Boulder
% \and
% Bo Waggoner\\
% \texttt{bwag@colorado.edu}\\
%  University of Colorado Boulder
%}
%%\date{%                          % nice hack
%%  % \vspace*{-5pt}
%%  University of Colorado Boulder
%%  \\[15pt]
%%  \today
%%}
\begin{document}
\title{An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates}
\author{\name Jessie Finocchiaro \email jefi8453@colorado.edu \\
	\addr Department of Computer Science\\
	University of Colorado Boulder\\
	Boulder, CO, USA
	\AND
	\name Rafael Frongillo \email raf@colorado.edu \\
	\addr Department of Computer Science\\
	University of Colorado Boulder\\
	Boulder, CO, USA
	\AND
	\name Bo Waggoner \email bwag@colorado.edu \\
	\addr Department of Computer Science\\
	University of Colorado Boulder\\
	Boulder, CO, USA
}

@@

\subsection{Surrogate regret bounds}\label{subsec:regret-bounds}
Recall that the approach of surrogate risk minimization is to learn a hypothesis $h$ that minimizes expected surrogate loss, then output hypothesis $\psi \circ h$, which hopefully minimizes expected target loss.
We would like surrogates where a bound on surrogate loss of $h$ immediately implies a bound on target loss of $\psi \circ h$.
One can formalize this problem in terms of \emph{regret}, as follows.
Fix a data distribution $\D$.
The \emph{surrogate regret} $\Reg_L$ of $h$ and the \emph{target regret} $\Reg_{\ell}$ of the implied hypothesis $\psi \circ h$, are given by
\begin{align*}
  \Reg_L(h;\D) &= \E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} \E_{(X,Y)\sim\D} L(h'(X))_Y~,
  \\
  \Reg_\ell(\psi\circ h;\D) &= \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{g':\X\to\R} \E_{(X,Y)\sim\D} \ell(g'(X))_Y~,
\end{align*}
% $\Reg_L(h;\D) = \E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} \E_{(X,Y)\sim\D} L(h'(X))_Y$,
where the infimum is taken over all measurable functions.
The infimum represents the risk of the Bayes optimal hypothesis, so regret can be viewed as \emph{excess risk} under the assumption that the learner's hypothesis class contains the Bayes optimal.
%(One may equivalently assume the Bayes optimal hypothesis is in the function class.)
% Given $h$, the \emph{target regret} of the implied hypothesis $\psi \circ h$ is $\Reg_\ell(\psi\circ h;\D) = \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} \E_{(X,Y)\sim\D} \ell(h'(X))_Y$.

Consistency (Definition~\ref{def:consistency}) means that if the surrogate regret of $h$ converges to zero, then the target regret of $\psi \circ h$ does as well; in other words, $\Reg_L(h;\D) \to 0$ implies $\Reg_{\ell}(\psi \circ h;\D) \to 0$.
Consistency is therefore a minimal requirement; in general, we are also interested in the \emph{rate} at which the target regret diminishes, as a function of the number of data points $m$.
A \emph{regret transfer bound}, also called a \emph{surrogate regret bound}, gives a guarantee on the relationship between the rates of convergence of $\Reg_L$ and $\Reg_{\ell}$.
For example, a surrogate with a fast rate of convegence $\Reg_L \to 0$ as $m \to \infty$ is not very useful if we nevertheless have a slow rate $\Reg_{\ell} \to 0$.

We show that, for any polyhedral surrogate, the transfer is linear: if surrogate regret diminishes at a rate of $O(f(m))$, then the target rate is also $O(f(m))$.
In particular, fast convergence in surrogate regret implies fast convergence in target regret.
\begin{theorem}
  \label{thm:linear-regret-bound}
  Let $(L,\psi)$ be consistent for a discrete loss $\ell$, and $L$ polyhedral.
  Then there exists $c > 0$ such that, for all measurable hypotheses $h$ and data distributions $\D$, we have $\Reg_{\ell}(\psi \circ h;\D) \leq c \cdot \Reg_L(h;\D)$.
\end{theorem}
In the proof (\S~\ref{app:regret-bounds}), we further show that the constant $c$ can be decomposed in terms of three constants, which depend on $L$, $\psi$, and $\ell$, respectively.
Specifically, we may write $c = C_\ell H_L / \epsilon_\psi$, where $H_L$ is the Hoffman constant for $L$, $\epsilon_\psi$ the separation of $\psi$, and $C_\ell$ the maximum loss gap of $\ell$.
This expression gives the intuition that larger link separation is generally better for performance.
In some cases, this bound can be tightened, as we discuss in \S~\ref{sec:regret-tighter-bounds}.
See \citet{frongillo2021surrogate} for a quadratic lower bound on the rate transfer for sufficiently non-polyhedral surrogates.

@@

Throughout we will work with the two \emph{regret} functions:
the \emph{surrogate regret} $\Reg_L(u,p) = \inprod{p}{L(u)} - \risk{L}(p)$, and similarly the \emph{target regret} $\Reg_{\ell}(r,p) = \inprod{p}{\ell(r)} - \risk{\ell}(p)$.
We will use these functions again when we prove surrogate regret bounds (\S~\ref{app:regret-bounds}).
% In fact, the results in this section can be extended to surrogate regret bounds; see \citet{frongillo2021surrogate}.

@@

\begin{lemma}\label{lem:hoffman-polyhedral}
  Let $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral loss with $\Gamma = \prop{L}$.
  Then for any fixed $p$, there exists some smallest constant $H_{L,p} \geq 0$ such that $d_{\infty}(u,\Gamma(p)) \leq H_{L,p} \Reg_L(u,p)$ for all $u \in \reals^d$.
\end{lemma}
\begin{proof}
  Since $L$ is polyhedral, there exist $a_1,\ldots,a_m \in \reals^d$ and $c\in\reals^m$ such that we may write $\inprod{p}{L(u)} = \max_{1\leq j\leq m} a_j \cdot u + c_j$.
  Let $A \in \reals^{m\times d}$ be the matrix with rows $a_j$, and let $b = \risk{L}(p)\ones - c$, where $\ones\in\reals^m$ is the all-ones vector.
  Then we have
  \begin{align*}
    S(A,b)
    &:= \{u\in\reals^d \mid A u \leq b\}
    \\
    &= \{u\in\reals^d \mid A u + c \leq \risk{L}(p)\ones\}
    \\
    &= \{u\in\reals^d \mid \forall i\, (A u + c)_i \leq \risk{L}(p)\}
    \\
    &= \{u\in\reals^d \mid \max_i \;(A u + c)_i \leq \risk{L}(p)\}
    \\
    &= \{u\in\reals^d \mid \inprod{p}{L(u)} \leq \risk{L}(p)\}
    \\
    & = \Gamma(p)~.
  \end{align*}
  Similarly, we have $\max_i\; (A u - b)_i = \inprod{p}{L(u)} - \risk{L}(p) = \regret{L}{u}{p} \geq 0$.
  Thus,
  \begin{align*}
    \|(Au - b)_+\|_\infty
    &= \max_i\; ((Au - b)_+)_i
    \\
    &= \max((Au - b)_1,\ldots,(Au - b)_m, 0)
    \\
    &= \max(\max_i\; (Au - b)_i, \, 0)
    \\
    &= \max_i\; (Au - b)_i
    % \\
    % &= \inprod{p}{L(u)} - \risk{L}(p)
    \\
    &= \regret{L}{u}{p}~.
  \end{align*}
  Now applying Theorem~\ref{thm:hoffman}, we have
  \begin{align*}
    d_\infty(u,\Gamma(p))
    &=    d_\infty(u,S(A,b))
    \\
    &\leq H(A) \, \|(Au-b)_+\|_\infty
    \\
    &= H(A) \, \regret{L}{u}{p}~.
  \end{align*}
\end{proof}

Given discrete loss $\ell: \R \to \reals_+^{\Y}$, define the constant $C_{\ell} = \max_{r,r' \in \R, y \in \Y} \ell(r)_y - \ell(r')_y$.
We are now ready to prove Theorem \ref{thm:calibrated-separated}.
\calibratedseparated*
\begin{proof}
  Let $\gamma=\prop{\ell}$ and $\Gamma=\prop{L}$.
  From Lemma~\ref{lem:calibrated-eps-sep}, calibration implies $\epsilon$-separation.
  For the converse, suppose $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$.
  Fix $p\in\simplex$.
  To show calibration, it suffices to find a positive lower bound for $\Reg_L(u,p)$ that holds for all $u\in\reals^d$ with $\psi(u) \notin \gamma(p)$.

  Applying the definition of $\epsilon$-separated and Lemma~\ref{lem:hoffman-polyhedral}, $\psi(u) \notin \gamma(p)$ implies
  \begin{align*}
    \epsilon &\leq    d_{\infty}(u,\Gamma(p)) \leq H_{L,p} \Reg_L(u,p) \implies 1 \leq \frac{H_{L,p}}{\epsilon} \Reg_L(u,p)~.
  \end{align*}
  Let $C_{\ell} = \max_{r,p} \Reg_{\ell}(r,p)$.
  Then $\Reg_{\ell}(\psi(u),p) \leq C_{\ell} \leq \frac{C_{\ell} H_{L,p}}{\epsilon} \Reg_L(u,p)$.

  If $H_{L,p} = 0$, then for all $u\in\reals^d$ we have $\Reg_\ell(\psi(u),p) = 0$, so calibration for this $p$ is trivial.
  \btw{In fact, we must also have $\Gamma(p) = \reals^d$ by Lemma~\ref{lem:hoffman-polyhedral}, since every $u\in\reals^d$ would have $d_\infty(u,\Gamma(p)) = 0$ and $\Gamma(p)$ is closed.}
  Similarly, if $C_\ell = 0$, then $\Reg_\ell(r,p) = 0$ for all $r\in\R$, so again $\Reg_\ell(\psi(u),p) = 0$ for all $u\in\reals^d$.

  Now assume $C_\ell > 0$ and $H_{L,p} > 0$.
  Let $C'_{\ell,p} \doteq \min_{r \notin \gamma(p)} \Reg_\ell(r,p) > 0$.
  (As we assume $C_\ell > 0$, we must have $\gamma(p) \neq \R$, so the minimum is attained.)
  Then for all $u$ such that $\psi(u) \notin \gamma(p)$, we have $\Reg_\ell(\psi(u),p) \geq C'_{\ell,p}$.
  Rearranging, we have
  \[ \psi(u) \notin \gamma(p) \implies \Reg_L(u,p) \geq \frac{C'_{\ell,p} \epsilon}{C_\ell H_{L,p}} > 0~.\]
  Thus, $\inf_{u : \psi(u) \notin \gamma(p)} \inprod{L(u)}{p} > \risk{L}(p)$.
  Since the above holds for all $p\in\simplex$, $\psi$ is calibrated.
\end{proof}

@@

\subsection{Proof of Theorem~\ref{thm:linear-regret-bound}}
% The following is a direct result of Jensen's inequality, using the fact that $\Reg_L(h;\D) = \E_X \Reg_L(h(X),p_X)$ where $p_X$ is the conditional distribution on $Y$ given $X$.
% \begin{observation} \label{obs:transfer}
%   If $(L,\psi)$ guarantee a conditional regret transfer of $\zeta$ for $\ell$, and $\zeta$ is concave, then $(L,\psi)$ guarantee a regret transfer of $\zeta$ for $\ell$.
% \end{observation}

\begin{lemma}\label{lem:linear-on-levelset}
  Suppose $(L,\psi)$ indirectly elicits $\ell$ and let $\Gamma = \prop{L}$.
  Then for any fixed $u,u^* \in \reals^d$ and $r \in \R$, the functions $\Reg_L(u,\cdot)$ and $\Reg_{\ell}(r,\cdot)$ are linear in their second arguments on $\Gamma_{u^*}$.
\end{lemma}
\begin{proof}
  Let $u^* \in \reals^d$ and $p \in \Gamma_{u^*}$.
  By definition, for all $p \in \Gamma_{u^*}$, $\risk{L}(p) = \inprod{p}{L(u^*)}$.
  So for fixed $u$,
    \[ \Reg_L(u,p) = \inprod{p}{L(u)} - \inprod{p}{L(u^*)} = \inprod{p}{L(u) - L(u^*)} , \]
  a linear function of $p$ on $\Gamma_{u^*}$.
  Next, by the definition of indirect elicitation, there exists $r^*$ such that $\Gamma_{u^*} \subseteq \gamma_{r^*}$.
  By the same argument, for fixed $r$, $\Reg_{\ell}(r,p) = \inprod{p}{\ell(r) - \ell(r^*)}$, a linear function of $p$ on $\gamma_{r^*}$ and thus on $\Gamma_{u^*}$.
\end{proof}

@@

\begin{lemma}\label{lem:separated-constant-p}
  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss, $L: \reals^d \to \reals_+^{\Y}$ be a polyhedral surrogate loss, and $\psi: \reals^d \to \R$ a link function.
  If $(L,\psi)$ indirectly elicit $\ell$ and $\psi$ is $\epsilon$-separated, then for all $u$ and $p$,
    \[ \Reg_{\ell}(\psi(u),p) \leq \frac{C_{\ell} H_{L,p}}{\epsilon} \Reg_L(u,p) . \]
\end{lemma}
\begin{proof}
  If $\psi(u) \in \gamma(p)$, then $\Reg_{\ell}(u,p) = 0$ and we are done.
  Otherwise, applying the definition of $\epsilon$-separated and Lemma~\ref{lem:hoffman-polyhedral},
  \begin{align*}
    \epsilon &<    d_{\infty}(u,\Gamma(p))  \\
             &\leq H_{L,p} \Reg_L(u,p) .
  \end{align*}
  So $\Reg_{\ell}(\psi(u),p) \leq C_{\ell} \leq \frac{C_{\ell} H_{L,p}}{\epsilon} \Reg_L(u,p)$.
\end{proof}

We can now restate and prove Theorem~\ref{thm:linear-regret-bound}.
\begin{theorem}[Theorem~\ref{thm:linear-regret-bound}]
  Let $\ell: \R \to \reals_+^{\Y}$ be discrete, $L: \reals^d \to \reals_+^{\Y}$ polyhedral, and $\psi: \reals^d \to \R$.
  If $(L,\psi)$ are consistent for $\ell$, then there exists constants $\epsilon_\psi, H_L > 0$ such that
    \[ (\forall h,\D) \quad \Reg_{\ell}(\psi \circ h ; \D) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} \Reg_L(h ; \D) ~. \]
\end{theorem}
\begin{proof}
  Let $\Gamma = \prop{L}$.
  From Lemma~\ref{lem:X}, there is a finite set $U \subset \reals^d$ of predictions such that (a) for each $u \in U$, the level set $\Gamma_u$ is a polytope (see e.g.\ Lemma~\ref{lem:level-set-is-projected-face}), and (b) $\cup_{u \in U} \Gamma_u = \simplex$.
  For each $u\in U$ let $\mathcal{Q}_u \subset \simplex$ be the finite set of vertices of the polytope $\Gamma_u$, and define the finite set $\mathcal{Q} = \cup_{u \in U} \mathcal{Q}_u$.
  Let $H_L := \max_{q\in\mathcal{Q}} H_{L,q}$.

  By Lemma~\ref{lem:calibrated-eps-sep}, $\psi$ is $\epsilon$-separated for some $\epsilon>0$; let $\epsilon_{\psi} = \epsilon$.
  By Lemma~\ref{lem:separated-constant-p}, for each $q \in \mathcal{Q}$,
  \[ \Reg_{\ell}(\psi(u),q) \leq \frac{C_{\ell} H_{L,q}}{\epsilon_{\psi}} \Reg_L(u,q) \leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} \Reg_L(u,q)\]
  for all $u\in\reals^d$.
  Now consider a general $p \in \simplex$, which is in some full-dimensional polytope level set $\Gamma_u$.
  Write $p = \sum_{q \in \mathcal{Q}_u} \beta(q) q$ for some convex combination $\beta \in \Delta_{\mathcal Q_u}$.
  By Lemma~\ref{lem:linear-on-levelset}, $\Reg_L$ and $\Reg_{\ell}$ are linear in the second argument on $\Gamma_u$, so for any $u'\in\reals^d$,
  \begin{align*}
    \Reg_{\ell}(\psi(u'),p)
    &=    \sum_{q \in \mathcal{Q}_u} \beta(q) \Reg_{\ell}(\psi(u'), q)  \\
    &\leq \sum_{q \in \mathcal{Q}_u} \beta(q) \frac{C_{\ell} H_{L}}{\epsilon_{\psi}} \Reg_L(u', q) \\
    &\leq \frac{C_{\ell} H_L}{\epsilon_{\psi}} \sum_{q \in \mathcal{Q}_u} \beta(q) \Reg_L(u', q)  \\
    &= \frac{C_{\ell} H_L}{\epsilon_{\psi}} \Reg_L(u', p) .
  \end{align*}
  The result for $\D$ now holds by linearity of expectation over $\D$.
  % \raf{Replace this last line (and preamble above) with a direct calculation -- don't need the observation, since we are actually linear!}
  % By Observation~\ref{obs:transfer}, this conditional regret transfer implies a full regret transfer, with the same constant.
\end{proof}
